\documentclass[11pt]{article}
\usepackage{times}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{natbib}
\usepackage{inconsolata}
\usepackage{palatino}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage[font=small]{caption}
\usepackage{longtable}
\bibliographystyle{abbrv}

\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=black,
  citecolor=black,
  allbordercolors=[rgb]{1.0,1.0,1.0},
}


\def\bibfont{\small}

\usepackage[compact]{titlesec}
% \titleformat{\section}{\normalfont\fontsize{14}{14}\bfseries}{\thesection}{}{\vspace{-1em}{\vspace{0em}}}
% \titleformat{\subsection}{\normalfont\fontsize{12}{12}\bfseries}{\thesubsection}{}{\vspace{-1em}{\vspace{0em}}
% \titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries}{\theparagraph}{0.5em}{}
% \titlespacing*\paragraph{0pt}{0.5em plus 2pt minus 2pt}{0.5em plus 2pt minus 2pt}
\setlength{\bibsep}{0pt plus 0.3ex}

\newcommand{\eg}{e.g., }
\newcommand{\todo}[1]{\textcolor{red}{#1}}
\newcommand{\daniel}[1]{\textcolor{blue}{DF: #1}}
\newcommand{\dfried}[1]{\textcolor{blue}{DF: #1}}

\title{\vspace{-4em}Daniel Fried: Evidence of External Reputation\vspace{-0.5em}}

\date{}


\begin{document}

\maketitle

\section*{Citations and Awards}
%\begin{longtable}{@{\hspace*{-3pt}}lr}
% \begin{tabular}{lr}
\begin{itemize}
    \item Okawa Research Award, 2023 
    \item Google Ph.D.\ Fellowship in Natural Language Processing, 2019 -- 2021 
    \item Outstanding Graduate Student Instructor, UC Berkeley, 2018 
    \item Outstanding Reviewer, ACL, 2018, 2020, 2021, 2022 
    \item Outstanding Reviewer, NeurIPS, 2019 
    \item Tencent AI Lab Fellowship, 2018 -- 2019 
    \item Huawei and Berkeley AI Fellowship, 2017 -- 2018 
    \item Best M.Phil.\ Student Award, Cambridge Computer Laboratory, 2015 
    \item Churchill Scholarship, 2014 -- 2015 
    \item NDSEG Fellowship, 2014 
    % Finalist, Hertz Graduate Fellowship & 2014 \\
    % Outstanding Senior Award in Research, U. Arizona College of Science & 2014 \\
    % Outstanding Senior Award in Academics, U. Arizona Computer Science & 2014 \\
    % Outstanding Senior Award in Academics, U. Arizona Information Science & 2014 \\
    %Pillars of Excellence Award, U. Arizona Honors College & 2014 \\
    % Barry M. Goldwater Scholarship & 2013 \\
    % Summer Research Fellowship, RWTH Aachen & 201 \\
    % Galileo Scholarship, U. Arizona College of Science & 2013 -- 2014 \\
    % National Merit Scholar & 2010 -- 2014 \\
    % Flinn Scholarship, Flinn Foundation of Arizona & 2010 -- 2014 \\
    % Watson Scholarship, IBM & 2010-2014 \\
    % Presidential Scholar, U.S. Department of Education & 2010 \\
%\end{longtable}
\end{itemize}
%\end{tabular}

\section*{Invited Talks}

\begin{itemize}
\item \emph{TBD}. Visually Grounded Interaction and Language (ViGIL) Workshop, ACL 2024
\item \emph{Interacting with LLMs for Grounded Tasks}. NILLI Workshop, EMNLP 2023. Spring 2023
\item \emph{Interacting with (code) LLMs}. MIT Neurosymbolic Reading Group. Spring 2023
\item \emph{InCoder, SantaCoder, and StarCoder: Findings from Training Open-Source Code LLMs}. Bloomberg AI; GitHub Next. Spring 2023
\item \emph{Using Language Strategically in Context}. CoRL Workshop on Strategic Multi-Agent Interactions, 2022; Johns Hopkins University, University of Pennsylvania, UT Austin. Spring 2023
\item \emph{Contextual Communication in Programming}. LTI Future of Code Generation Seminar, 2022
\item \emph{Reasoning About Actions and Rewards in Language Interactions}. MIT CPL, 2022. (with Jessy Lin)
\item \emph{Modularity in Grounded Interaction}. ViGIL Workshop, NAACL 2021. (with Rudy Corona)
\item \emph{Learning Grounded Pragmatic Communication}. University of Arizona, TTI-Chicago, University of Southern California, Purdue, Carnegie Mellon University, UC Irvine, Université de Montréal/Mila, Allen Institute for Artificial Intelligence, Facebook AI Research, Google Research, Stanford Cognition and Language Workshop. Spring 2021
\item \emph{Pragmatic Models for Generating and Following Grounded Instructions}. Stanford NLP Seminar, University of Arizona, USC ISI. Fall 2018--Spring 2019
\end{itemize}

\end{document}
