\section{}

\begin{enumerate}[leftmargin=-1mm,partopsep=0pt]

\item[]\hspace{-7em}{\small \sc \textbf{Refereed Journal Papers - Published}}

\item Raymond Li et al. (68 authors from the BigCode Project) (2023). StarCoder: May the Source Be With You!. In \emph{Transactions on Machine Learning Research (TMLR)}.

\item FAIR Diplomacy Team (2022). Human-Level Play in the Game of Diplomacy by Combining Language Models with Strategic Reasoning. In \emph{Science}.

\item Adhiguna Kuncoro*, Lingpeng Kong*, \underline{Daniel Fried}*, Dani Yogatama, Laura Rimell, Chris Dyer, and Phil Blunsom (2020). Syntactic Structure Distillation Pretraining for Bidirectional Encoders. In \emph{Transactions of the Association for Computational Linguistics (TACL)}.

\item \underline{Daniel Fried}, Peter Jansen, Gustave Hahn-Powell, Mihai Surdeanu, and Peter Clark (2015). Higher-Order Lexical Semantic Models for Non-Factoid Answer Reranking. In \emph{Transactions of the Association for Computational Linguistics (TACL)}.

\item[]\hspace{-7em}{\small \sc \textbf{Refereed Conference / Workshop Papers}}

\item Shenghui Chen, \underline{Daniel Fried}, and Ufuk Topcu (2024). Human-Agent Cooperation in Games under Incomplete Information through Natual Language Communication . In \textbf{International Joint Conference on Artificial Intelligence (IJCAI)}.

\item Andy Liu, Mona T. Diab, and \underline{Daniel Fried} (2024). Evaluating Large Language Model Biases in Person-Steered Generation. In \textbf{Findings of ACL}.

\item Akhila Yerukola, Saujas Vaduguru, \underline{Daniel Fried}, and Maarten Sap (2024). Is the Pope Catholic? Yes, the Pope is Catholic. Generative Evaluation of Intent Resolution in LLMs. In \textbf{Annual Meeting of the Association for Computational Linguistics (ACL)}.

\item Jing Yu Koh, Robert Lo*, Lawrence Jang*, Vikram Duvvur*, Ming Chong Lim*, Po-Yu Huang*, Graham Neubig, Shuyan Zhou, Ruslan Salakhutdinov, and \underline{Daniel Fried} (2024). VisualWebArena: Evaluating Multimodal Agents on Realistic Visual Web Tasks. In \textbf{Annual Meeting of the Association for Computational Linguistics (ACL)}.

\item Zhiruo Wang, Graham Neubig, and \underline{Daniel Fried} (2024). TroVE: Inducing Verifiable and Efficient Toolboxes for Solving Programmatic Tasks. In \textbf{International Conference on Machine Learning (ICML)}.

\item Yewen Pu, Saujas Vaduguru, Priyan Vaithilingam, Elena Glassman, and \underline{Daniel Fried} (2024). Amortizing Pragmatic Program Synthesis with Rankings. In \textbf{International Conference on Machine Learning (ICML)}.

\item Sedrick Keh, Justin T. Chiu, and \underline{Daniel Fried} (2024). Asking More Informative Questions for Grounded Retrieval. In \textbf{Findings of NAACL}.

\item Saujas Vaduguru, \underline{Daniel Fried}, and Yewen Pu (2024). Generating Pragmatic Examples to Train Neural Program Synthesizers. In \textbf{International Conference on Learning Representations (ICLR)}.

\item Xuhui Zhou*, Hao Zhu*, Leena Mathur, Ruohong Zhang, Haofei Yu, Zhengyang Qi, Louis-Philippe Morency, Yonatan Bisk, \underline{Daniel Fried}, Graham Neubig, and Maarten Sap (2024). Sotopia: Interactive Evaluation for Social Intelligence in Language Agents. In \textbf{International Conference on Learning Representations (ICLR)}.

\item Shuyan Zhou*, Frank Xu*, Hao Zhu**, Xuhui Zhou**, Robert Lo**, Abishek Sridhar**, Xianyi Cheng, Yonatan Bisk, \underline{Daniel Fried}, Uri Alon, and Graham Neubig (2024). WebArena: A Realistic Web Environment for Building Autonomous Agents. In \textbf{International Conference on Learning Representations (ICLR)}.

\item Yihan Cao*, Shuyi Chen*, Ryan Liu*, Zhiruo Wang, and \underline{Daniel Fried} (2023). API-Assisted Code Generation for Question Answering on Varied Table Structures. In \textbf{Empirical Methods in Natural Language Processing (EMNLP)}.

\item Justin Chiu, Wenting Zhao, Derek Chen, Saujas Vaduguru, Alexander Rush, and \underline{Daniel Fried} (2023). Symbolic Planning and Code Generation for Grounded Dialogue . In \textbf{Empirical Methods in Natural Language Processing (EMNLP)}.

\item \underline{Daniel Fried}*, Nicholas Tomlin*, Jennifer Hu, Roma Patel, and Aida Nematzadeh (2023). Pragmatics in Language Grounding: Phenomena, Tasks, and Modeling Approaches. In \textbf{Findings of EMNLP}.

\item Zhiruo Wang, Shuyan Zhou, \underline{Daniel Fried}, and Graham Neubig (2023). Execution-Based Evaluation for Open-Domain Code Generation. In \textbf{Findings of EMNLP}.

\item Yiqing Xie, Atharva Naik, \underline{Daniel Fried}, Carolyn Rose (2023). Data Augmentation for Code Translation with Comparable Corpora and Multiple References. In \textbf{Findings of EMNLP}.

\item Weiyan Shi, Emily Dinan, Adi Renduchintala, \underline{Daniel Fried}, Athul Paul Jacob, Zhou Yu, and Mike Lewis (2023). AutoReply: Detecting Nonsense in Dialogue Introspectively with Discriminative Replies. In \textbf{Findings of EMNLP}.

\item Jing Yu Koh, \underline{Daniel Fried}, and Ruslan Salakhutdinov (2023). Generating Images with Multimodal Language Models. In \textbf{Neural Information Processing Systems (NeurIPS)}.

\item Jiefu Ou, Benno Krojer, and \underline{Daniel Fried} (2023). Pragmatic Inference with a CLIP Listener for Contrastive Captioning. In \textbf{Findings of ACL}.

\item Xiang Lisa Li, Ari Holtzman, \underline{Daniel Fried}, Percy Liang, Jason Eisner, Tatsunori Hashimoto, Luke Zettlemoyer, and Mike Lewis (2023). Contrastive Decoding: Open-ended Text Generation as Optimization. In \textbf{Annual Meeting of the Association for Computational Linguistics (ACL)}.

\item Jing Yu Koh, Ruslan Salakhutdinov, and \underline{Daniel Fried} (2023). Grounding Language Models to Images for Multimodal Inputs and Outputs. In \textbf{International Conference on Machine Learning (ICML)}.

\item Tianyi Zhang, Tao Yu, Tatsunori B. Hashimoto, Mike Lewis, Wen-tau Yih, \underline{Daniel Fried}, and Sida I. Wang (2023). Coder Reviewer Reranking for Code Generation. In \textbf{International Conference on Machine Learning (ICML)}.

\item Yuhang Lai*, Chengxi Li*, Yiming Wang*, Tianyi Zhang*, Ruiqi Zhong*, Luke Zettlemoyer, Scott Wen-tau Yih, \underline{Daniel Fried}, Sida I. Wang, and Tao Yu (2023). DS-1000: A Natural and Reliable Benchmark for Data Science Code Generation. In \textbf{International Conference on Machine Learning (ICML)}.

\item \underline{Daniel Fried}*, Armen Aghajanyan*, Jessy Lin, Sida I. Wang, Eric Wallace, Freda Shi, Ruiqi Zhong, Wen-tau Yih, Luke Zettlemoyer, and Mike Lewis (2023). InCoder: A Generative Model for Code Infilling and Synthesis. In \textbf{International Conference on Learning Representations (ICLR)}.

\item Loubna Ben Allal*, Raymond Li*, Denis Kocetkov*, et al. (41 authors from the BigCode Project) (2023). SantaCoder: Don't Reach for the Stars. In \textbf{Deep Learning for Code Workshop}.

\item Freda Shi, \underline{Daniel Fried}, Marjan Ghazvininejad, Luke Zettlemoyer, and Sida I. Wang (2022). Natural Language to Code Translation with Execution. In \textbf{Empirical Methods in Natural Language Processing (EMNLP)}.

\item Maarten Sap, Ronan Le Bras, \underline{Daniel Fried}, and Yejin Choi  (2022). Neural Theory-of-Mind? On the Limits of Social Intelligence in Large LMs. In \textbf{Empirical Methods in Natural Language Processing (EMNLP)}.

\item Grace Luo*, Giscard Biamby*, Trevor Darrell, \underline{Daniel Fried}, and Anna Rohrbach (2022). G3: Geolocation via Guidebook Grounding. In \textbf{Findings of EMNLP}.

\item Jessy Lin, \underline{Daniel Fried}, Dan Klein, and Anca Dragan (2022). Inferring Rewards from Language in Context. In \textbf{Annual Meeting of the Association for Computational Linguistics (ACL)}.

\item Justin Chiu, Wenting Zhao, Alexander M. Rush, and \underline{Daniel Fried} (2022). Modeling Perspective-Dependent Ambiguity in Grounded Collaborative Dialogue. In \textbf{Wordplay: When Language Meets Games Workshop}.

\item \underline{Daniel Fried}, Justin Chiu, and Dan Klein (2021). Reference-Centric Models for Grounded Collaborative Dialogue. In \textbf{Empirical Methods in Natural Language Processing (EMNLP)}.

\item Rodolfo Corona, \underline{Daniel Fried}, Coline Devin, Dan Klein, and Trevor Darrell (2021). Modular Networks for Compositional Instruction Following. In \textbf{North American Chapter of the Association for Computational Linguistics (NAACL)}.

\item David Gaddy, \underline{Daniel Fried}, Nikita Kitaev, Mitchell Stern, Rodolfo Corona, John DeNero, and Dan Klein (2021). Interactive Assignments for Teaching Structured Neural NLP. In \textbf{Teaching NLP Workshop at NAACL}.

\item \underline{Daniel Fried}, Jean-Baptiste Alayrac, Phil Blunsom, Chris Dyer, Stephen Clark, Aida Nematzadeh (2020). Learning to Segment Actions from Observation and Narration. In \textbf{Annual Meeting of the Association for Computational Linguistics (ACL)}.

\item \underline{Daniel Fried}*, Nikita Kitaev*, and Dan Klein (2019). Cross-Domain Generalization of Neural Constituency Parsers. In \textbf{Annual Meeting of the Association for Computational Linguistics (ACL)}.

\item Ronghang Hu, \underline{Daniel Fried}, Anna Rohrbach, Dan Klein, Trevor Darrell, and Kate Saenko (2019). Are You Looking? Grounding to Multiple Modalities in Vision-and-Language Navigation. In \textbf{Annual Meeting of the Association for Computational Linguistics (ACL)}.

\item Sheng Shen, \underline{Daniel Fried}, Jacob Andreas, and Dan Klein (2019). Pragmatically Informative Text Generation. In \textbf{North American Chapter of the Association for Computational Linguistics (NAACL)}.

\item \underline{Daniel Fried}*, Ronghang Hu*, Volkan Cirik*, Anna Rohrbach, Jacob Andreas, Louis-Philippe Morency, Taylor Berg-Kirkpatrick, Kate Saenko, Dan Klein**, and Trevor Darrell**  (2018). Speaker-Follower Models for Vision-and-Language Navigation. In \textbf{Neural Information Processing Systems (NeurIPS)}.

\item \underline{Daniel Fried} and Dan Klein (2018). Policy Gradient as a Proxy for Dynamic Oracles in Constituency Parsing. In \textbf{Annual Meeting of the Association for Computational Linguistics (ACL)}.

\item \underline{Daniel Fried}, Jacob Andreas, and Dan Klein (2018). Unified Pragmatic Models for Generating and Following Instructions. In \textbf{North American Chapter of the Association for Computational Linguistics (NAACL)}.

\item Mitchell Stern, \underline{Daniel Fried}, and Dan Klein (2017). Effective Inference for Generative Neural Parsing. In \textbf{Empirical Methods in Natural Language Processing (EMNLP)}.

\item \underline{Daniel Fried}*, Mitchell Stern*, and Dan Klein (2017). Improving Neural Parsing by Disentangling Model Combination and Reranking Effects. In \textbf{Annual Meeting of the Association for Computational Linguistics (ACL)}.

\item Dane Bell, \underline{Daniel Fried}, Luwen Huangfu, Mihai Surdeanu, and Stephen Kobourov (2016). Towards Using Social Media to Identify Individuals at Risk for Preventable Chronic Illness. In \textbf{Language Resources and Evaluation Conference (LREC)}.

\item Dane Bell, \underline{Daniel Fried}, Luwen Huangfu, Mihai Surdeanu, and Stephen (2016). Challenges for Using Social Media for Early Detection of Type II Diabetes Mellitus. In \textbf{International Workshop on Social Media World Sensors}.

\item \underline{Daniel Fried}, Tamara Polajnar, and Stephen Clark (2015). Low-Rank Tensors for Verbs in Compositional Distributional Semantics. In \textbf{Annual Meeting of the Association for Computational Linguistics (ACL)}.

\item \underline{Daniel Fried}, Tamara Polajnar, and Stephen Clark (2015). Learning Low-Rank Tensors for Transitive Verbs. In \textbf{Advances in Distributional Semantics Workshop}.

\item \underline{Daniel Fried} and Kevin Duh (2015). Incorporating both Distributional and Relational Semantics in Word Representations. In \textbf{International Conference on Learning Representations (ICLR) Workshop}.

\item \underline{Daniel Fried}, Mihai Surdeanu, Stephen Kobourov, Melanie Hingle, and Dane Bell (2014). Analyzing the Language of Food on Social Media. In \textbf{International Conference on Big Data}.

\item \underline{Daniel Fried} and Stephen Kobourov (2014). Maps of Computer Science. In \textbf{Pacific Visualization Symposium (PacificVis)}.

\item \underline{Daniel Fried}, Zhen Li, Ali Jannesari, and Felix Wolf (2013). Predicting Parallelization of Sequential Programs Using Supervised Learning. In \textbf{International Conference on Machine Learning and Applications}.

\item Colin Dawson, Jeremy Wright, Antons Rebguns, Marco Valenzuela Escarcega, \underline{Daniel Fried}, and Paul Cohen (2013). A Generative Probabilistic Framework for Learning Spatial Language. In \textbf{International Conference on Development and Learning}.

\item Luca Del Pero, Joshua Bowdish, \underline{Daniel Fried}, Bonnie Kermgard, Emily Hartley, and Kobus Barnard (2012). Bayesian Geometric Modeling of Indoor Scenes. In \textbf{Conference on Computer Vision and Pattern Recognition (CVPR)}.

\item[]\hspace{-7em}{\small \sc \textbf{Technical Reports}}

\item Yiqing Xie, Alex Xie, Divyanshu Sheth, Pengfei Liu, \underline{Daniel Fried}, and Carolyn Rose (2024). CodeBenchGen: Creating Scalable Execution-based Code Generation Benchmarks. In \emph{arXiv}.

\item Zora Zhiruo Wang, Zhoujun Cheng, Hao Zhu, \underline{Daniel Fried}, and Graham Neubig (2024). What Are Tools Anyway? A Survey from the Language Model Perspective. In \emph{arXiv}.

\item Jacob Mitchell Springer, Suhas Kotha, \underline{Daniel Fried}, Graham Neubig, and Aditi Raghunathan (2024). Repetition Improves Language Model Embeddings. In \emph{arXiv}.

\item Alex Wilf, Alex Tianyi Xu, Paul Pu Liang, Alexander Obolenskiy, \underline{Daniel Fried}, and Louis-Philippe Morency (2023). Comparative Knowledge Distillation. In \emph{arXiv}.

\end{enumerate}

\textbf{*,**}: equal contribution
